Multi sky-view\\ 3D aerosol distribution recovery

### 2013-10-02 article.tex
Yoav Changes
work on graphics

For example, consider a photon propagating in the atmosphere.  The
photon has high probability of propagating as long as $t$ is high, and
the probability diminishes as $t\rightarrow 0$. Thus
(\cref{eq:beer-lambert}) can be viewed as a probability density
function, whose CDF is
\begin{equation}
  \label{eq:Ftau}
  F(\tau)=\int_{0}^{\tau}\exp(-\tau')\derivsym{\tau'}=1-\exp(-\tau).
\end{equation}
Thus a photon propagates to a random optical depth
\begin{equation}
  \label{eq:taurand}
  \tau^{\rm random}=F^{-1}(u)=-\ln(1-u).
\end{equation}
If the atmosphere is uniform, then from \cref{eq:tau} the photon
reaches a random distance
\begin{equation}
  \label{eq:lrand}
  l^{\rm random}= (\beta^{\rm aerosol}+\beta^{\rm air})^{-1} \tau^{\rm random}
  = -(\beta^{\rm aerosol}+\beta^{\rm air})^{-1}\ln(1-u),
\end{equation}
before interacting with a particle. If the number of photons launched
is very high, their average number falls off in consistency with
\cref{eq:tau,eq:beer-lambert}.  Analogous transforms
generate scattering at random angles, according to the phase function.

@@

\Cref{fig:scatter_order} \hl{shows the contribution of subsequent
scattering events to the MC image. The amount of light scattered
in the direction of the sun due to the first scatter event of each photon
is collected to create} \cref{fig:scatter_order}(a). \hl{This process
is repeated for the second and third scatter events creating}
\cref{fig:scatter_order}(b) and \cref{fig:scatter_order}(c),
\hl{respectively. It is conspicuous that the first scatter is responsible
for most of the energy in the MC image. The effect of subsequent scatters
is mostly evident at the horizon. The line of sight extending into the
horizon crosses a larger volume of atmosphere then the line of sight extending
in the direction of the zenith. This increases the probability of
scattering events along the line of sight extending into the horizon.}
\begin{figure}[h]
  \centering
  \yoavcomment{\includegraphics{images/scatter_order.pdf}}
  \caption{\small Separation of a MC simulated image to (a) first
   scattering order, (b) second scattering order and (c) third
   scattering order. }
  \label{fig:scatter_order}
\end{figure}

>>>>

For example, consider a photon propagating in the atmosphere.  The
photon has high probability of propagating as long as $t$ is high, and
the probability diminishes as $t\rightarrow 0$. Thus
(\cref{eq:beer-lambert}) can be viewed as a probability density
function, whose CDF is
\begin{equation}
  \label{eq:Ftau}
  F(\tau)=\int_{0}^{\tau}\exp(-\tau')\derivsym{\tau'}=1-\exp(-\tau).
\end{equation}
Thus a photon propagates to a random optical depth
\begin{equation}
  \label{eq:taurand}
  \tau^{\rm random}=F^{-1}(u)=-\ln(1-u),
\end{equation}
where $F^{-1}$ denotes the inverse function of $F$.
If the atmosphere is uniform, then from \cref{eq:tau} the photon
reaches a random distance
\begin{equation}
  \label{eq:lrand}
  l^{\rm random}= (\beta^{\rm aerosol}+\beta^{\rm air})^{-1} \tau^{\rm random}
  = -(\beta^{\rm aerosol}+\beta^{\rm air})^{-1}\ln(1-u),
\end{equation}
before interacting with a particle. If the number of photons launched
is very high, their average number falls off in consistency with
\cref{eq:tau,eq:beer-lambert}.  Analogous transforms
generate scattering at random angles, according to the phase function.

@@

\Cref{fig:scatter_order} \hl{shows the contribution of subsequent
scattering events to the MC image. The amount of light scattered
in the direction of the sun due to the first scatter event of each photon
is collected to create} \cref{fig:scatter_order}(a). \hl{This process
is repeated for the second and third scatter events creating}
\cref{fig:scatter_order}(b) and \cref{fig:scatter_order}(c),
\hl{respectively. It is conspicuous that the first scatter is responsible
for most of the energy in the MC image. The effect of subsequent scatters
is mostly evident at the horizon. The line of sight extending into the
horizon crosses a larger volume of atmosphere then the line of sight extending
in the direction of the zenith. This increases the probability of
scattering events along the line of sight extending into the horizon.}
\begin{figure}[h]
  \centering
  \yoavcomment{\includegraphics{images/scatter_order.pdf}}
  \caption{\small Separation of a MC simulated image to (a) first
   scattering order, (b) second scattering order, (c) third
   scattering order and (d) forth scattering order. }
  \label{fig:scatter_order}
\end{figure}
